### 2015-01-21 paper.tex
more stuff

SAT solving is being used for many applications where

@@

% \begin{verbatim}
 \begin{lstlisting}
data Rule = Remove [Tag] Condition | Select [Tag] Condition

>>>>

SAT solving is used for many applications where constraints must be
satisfied, such as software and hardware verification.

\subsection{CG formulated in SAT}

We make each analysis a variable. For instance, the fifth line denotes
a hypothesis that the correct analysis of the 3rd item in the sentence
is \texttt{<V,Sg>}. We call this \texttt{Var 5}.

\begin{lstlisting}
((1,[Lem "the",Det]),Var 1)
((2,[Lem "bear",N,Sg]),Var 2)
((2,[Lem "bear",V,Pl]),Var 3)
((3,[Lem "sleep",N,Pl]),Var 4)
((3,[Lem "sleep",V,Sg]),Var 5)
((4,[Lem "in",Prep]),Var 6)
((4,[Lem "in",Adv]),Var 7)
((5,[Lem "the",Det]),Var 8)
((6,[Lem "house",V,Inf]),Var 9)
((6,[Lem "house",N,Sg]),Var 10)
\end{lstlisting}

We have defined our variables, but not yet any truth values. We can
start by doing two things:
\begin{enumerate}
\item Make unambiguous tokens true by default: e.g. \texttt{Var 1}
  shows that the reading \texttt{Det} for the first token must be true.
\item Make hypotheses of possible n-grams. In the example below, we
show bigrams: \texttt{(Var 1 $\wedge$ Var 2) $\vee$ (Var 1 $\wedge$ Var 3)}
means that the first two tokens have analyses \texttt{Det,N} or
\texttt{Det,V}.
\end{enumerate}

We could easily add a third rule: for ambiguous tokens, make sure that
only one reading can be true (or a less strict version, where all
readings can't be true). For instance, \texttt{Not (Var 2 $\wedge$ Var
  3)} would be the constraint that the second token can't be both
\texttt{N} and \texttt{V} at the same time. However,
\cite{KarlssonTODO} argues that CG cannot remove genuine ambiguities;
in a case where a sentence is genuinely ambiguous, all readings are
returned.

\begin{lstlisting}
Var 1
Var 8
(Var 1 :&&: Var 2) :||: (Var 1 :&&: Var 3)
(Var 2 :&&: Var 4) :||: ((Var 2 :&&: Var 5) :||: ((Var 3 :&&: Var 4) :||: (Var 3 :&&: Var 5)))
(Var 4 :&&: Var 6) :||: ((Var 4 :&&: Var 7) :||: ((Var 5 :&&: Var 6) :||: (Var 5 :&&: Var 7)))
(Var 6 :&&: Var 8) :||: (Var 7 :&&: Var 8)
(Var 8 :&&: Var 9) :||: ((Var 8 :&&: Var 10))
\end{lstlisting}
% Not (Var 2 :&&: Var 3)
% Not (Var 4 :&&: Var 5)
% Not (Var 6 :&&: Var 7)
% Not (Var 9 :&&: Var 10)

Another property of CG is that cannot remove all readings: if all
other analyses are eliminated, the remaining analysis must be
returned, even if it were to be eliminated at the next pass. 
However, this property isn't implemented in the SAT version.

@@

\begin{lstlisting}
data Rule = Remove [Tag] Condition | Select [Tag] Condition
